Investigating Predictors for American Attitudes on Justifiability of Abortion

### 2022-06-20 Final/FinalReport.qmd
fixed some captions

caption1 <- ggdraw() + 
  draw_label(
    "Fig.2: The visuals show that while some variables in the data set 
    have bell-shaped distributions, others are left-skewed.",
    x = 0,
    hjust = 0, 
    size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )

@@

caption4 <- ggdraw() + 
  draw_label("Fig.7: The linearity condition and constant variance condition 
             is clearly not met in this plot of residuals v. fitted values.",
    x = 0,
    hjust = 0, size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )
caption5 <- ggdraw() + 
  draw_label("Fig.8: The residuals appear to follow a normal distribution, 
             which looks like a bell-shape, as illustrated in red.",
    x = 0,
    hjust = 0, size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )
caption6 <- ggdraw() + 
  draw_label("Fig.9: The residuals plotted by observation order are randomly 
             scattered, showing no structure.",
    x = 0,
    hjust = 0, size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )

>>>>

caption1 <- ggdraw() + 
  draw_label(
    "Fig.2: The visuals show that while some variables have bell-shaped distributions, others are left-skewed.",
    x = 0,
    hjust = 0, 
    size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )

@@

caption4 <- ggdraw() + 
  draw_label(
"Fig.7: The linearity condition and constant variance condition is clearly not 
met in this plot of residuals v. fitted values.",
    x = 0,
    hjust = 0, size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )
caption5 <- ggdraw() + 
  draw_label(
"Fig.8: The residuals appear to follow a normal distribution, which looks like 
a bell-shape, as illustrated in red.",
    x = 0,
    hjust = 0, size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )
caption6 <- ggdraw() + 
  draw_label(
"Fig.9: The residuals plotted by observation order are randomly scattered, 
showing no structure.",
    x = 0,
    hjust = 0, size = 8
  ) +
  theme(
    plot.margin = margin(0, 0, 0, 7)
  )
